\section{Description of the Team, Partners and Collaborators}
%(500 words maximum)

Core Team

\begin{enumerate}
\item \textbf{Mark Santolucito} - Yale CS MA '15, PhD '19\\
    Game design, game development

\item \textbf{Dr. Maria Hwang} - Columbia University Medical Center Postdoc Researcher
	Usability Studies, Medical Theory, games for health design

\item \textbf{Rahul Dhodapkar} - Yale ‘15, MongoDB\\
	Technical infrastructure, medical industry
\end{enumerate}

Key Consultants

\begin{enumerate}
\item \textbf{Dao Chantes} - Columbia Teacher’s College Ed.D. Candidate\\
	Graphic Design, game design, game art

\item \textbf{Fiona Santolucito} - Johns Hopkins '16\\
	Play tester, community contact

\end{enumerate}

\begin{enumerate}
\itemsep-0.5em 

    \item How long have the founders known one another and how did you meet?
    \item Have any of the founders not met in person?
    \item What are the roles of your team members?
    \item Do you have domain expertise in this area?
    \item What is the gap in expertise in your team? Specifically, how do you plan to address that gap in the near term?
\end{enumerate}
%(500 words maximum starts here)

The founders have known each other for more than 2 years. Mark and Dr. Hwang collaborated on a games for health research project since 2013, resulting in Dr. Hwang's dissertation "Effectiveness of message framing in a digital game environment"~\cite{hwang2016}. Together, they designed, developed, and ran user tests on a game for behavior therapy of nutritional health.

Mark Santolucito is currently a Computer Science PhD student at Yale, expecting to graduate in 2019.
Mark's research focus is on developing programming languages for interactive systems, like games.
Using this expertise, Mark will be the primary developer for the game itself.

Rahul Dhodapkar, YC'15, is currently working as a consultant at MongoDB, an opensource database company.
He was a computer science major at Yale, where he took a number of classes with Mark (Category Theory, Complexity Theory, and Korean Language).
He will be a student at NYU in Spring 2017 to fulfill the requirements for a later application to medical school. 
His experience with databases will drive the analytics engine for the effectiveness studies. 

Dr. Maria Hwang is currently working as a postdoctoral researcher at Columbia University Medical School on games for health. We are drawing heavily on her expertise, access to facilities and test subjects, as well as professional connections.

One of the most important aspects of game development is graphic design. While the core team does not include a graphic designer, we plan to fill this gap by hiring Dao Chantes. Dao is the same graphic designer that collaborated on Maria's dissertation. Working with Dao was a very pleasant experience, and she is a talented and productive graphic designer. Our budget has allocated funds for this purpose. 

One additional resource we plan to draw on, is Fiona Santolucito, Mark's sister.
Fiona has recently went through a transition and is well-connected to the transgender community.

%All three of the founders and Dao Chantes, among others, also attended a week-long seminar in Korea in June 2016
