\section{How does your idea provide an innovative solution to the health challenge described above? 
What is your value proposition?}

(250 words maximum)    

%\textit{explains how your product solves customers’ problems or improves their situation (relevancy)}
Both transgender people and their family members go through a difficult time during a transition. The family may not understand what led to this, may be worried about their transgender family member's future, etc. The transgender people may not understand why their families are, in their eyes, not being fully supportive of their identity. We specifically wanted to target this misunderstanding and possible lack of communication based on this misunderstanding that occur amongst family members. 

%\textit{delivers specific benefits (quantified value)}
This app can help restore the family's relationship(s) and bring mutual understanding. It can also lead to a healthy communicative culture within the family that can be sustained beyond the beginning transition period. We do not want this to only be a temporary solution but a permanent one. 

%\textit{tells the ideal customer why they should buy from you and not from the competition (unique differentiation).}
Not all issues are solved via medication. Don't depend on medicating your family members to cure them, just let them play games. We are targeting both the transgender individual and his or her family members to play this game to establish a better ground for communication. No other company or establishment, best to our knowledge, includes games that target the family members in addition to the transgender individual. The psychological health of the entire family is where we believe is the area of significant medical need. 
%These are not issues to be solved by medicating your child to cure them, just let them play games.

%some phrases borrowed from here and there:
%"dedicated to developing innovations that address areas of significant medical need"