# 2016-11-22 Meeting Notes

Initial project

Maria is the **expert**

## Meetings

- Rick Hunt
    > Highlight technical capabilities

- IHY with Cass Walker
    > See a prototype of the game
    > Testing with real people
    > Great to be personally invested

- longterm goal - Games for change

- Contrast with Project Evo
   > not targeting medical conditions
   > targeting psychological therapy
   
## Asks

Nov 29 Aetna Seed Grant - \$10k
Dec 6 IHY Seed Grant - \$10k

**FAIRLY TIGHT**
- prototype
    > Does not need to be the same game
    > qualitative testing with friends
    > Take videos of gameplay
    > Quotes (like a pilot study)

## Action Items

 [Mark + Maria]
 - w/ Maria a game design. what quantitative measure do we want observe change in participant
    > see change in ability to empathize
    > related to info seeking behavior - asking questions about another person
    > find standardized, short psych battery [metric] 
       - downside is does not provide clear target that can inform game design

 [Mark]     
 - Start a unity project - Mark

 [Rahul]
 - Take a crack at filling out the Master plan
    > 
    > fill master

%%%%%%%%%%
what quantitative measure do we want to observe in our participants

having to want to OBSERVE change
(information seeking behaviour)

document : master plan (MP)
MP will be continuously updated
G4C

games for (mental) health

merely a tool to deal with a bigger issue(?)
not targeting medical conditions
targeting psychological therapy/adjustment
similar to Project Evo we want metrics that can be measured (to see change)

see the ability to empathize (related to ISB?)
** clicks on sites that have to do with trans issues
** Embedding metrics in game
** a neighbor kid needs consulting. needs money 
** the more you play the game, the greater the effect

association task. (point system, +1 for correct answers, -1 for incorrect)
time stamps
transitions 

what would the control look like: the game conditions do not change and nothing switches at all. 
switching pronouns
worries about the kids' future (raise a pokemon, it stops doing the things you tell it to do, pokemon stops listening to you but it still succeeds)

## Specific of Game Design

[Core Game Goal]
Target shape appears
Confounding shape appears

[Core Game Mechanic]
Shape or confounding shape flashes on screen, quickly, one at a time.
Clicking on target shape (ding)
Do not click on confounding shape (buzz)
Survival game, when score goes below 0, you lose
Interval gets progressively shorter
At the end, you will get a score for interval

- Number of phases (infinite)?
    > shuffle between series of randomly generated scenarios.

## Storyboard
1. Open up the game

2. Instructions
{}
    Aliens are attacking the earth, only the power gems can save humanity.
    
    We need to maintain a balance of gems in the Earth, and because they are mixed up, so you need to not mess up the fuel mix.
    
    Earth Defenders <Galaxy Grod>
{}


