# [v0.2] [2016-11-26] Interview w/ Io Oakes

What was difficult about the game?

    > difficult to understand (color blind people) **I noticed begin button is pretty obvious

    > 

What was easy about the game?

    > left and right (if there were only two colors)
    >
Do you think you are better at the game than when you started?

    >not really
    >
Why did you improve?

    > 
    >
Would you play again?

    > no
    >
General feedback

    > more than one color. (instruction was not clear that there would be multiple colors)
    >
    
    > summer before last, we were down here, jim como an old friend, and he is a very nice person, but very limited in his worldly. lots of things have happened to his family . and one of the big questions was that obvi fiona transitioned and she came walking with all of us and i dik who said it but, the question was how do you go out in the world and get a new identify. and what do you do. one thing that fiona said is put it all on facebook ad idk what she showed us was that so many people including teacher of hers, were o supportive of her and i thought that was wonderful . i think she was very happy about that. 
    
    > I wish she was more accepting of other transgender people and shes not. i think it would be helpful for her to be more accepting. theres lots of older people who are transition and she has problems with that and she has problem s with the way they are and behave. and she isnt very accepting. i wish she could be a little more accepting of other people who are "less" than her. it would help.
    
    > time and a lot of love and understanding from all the family
    
What was difficult about the transgender transition in your family?
What was easy about the transgender transition in your family?
Do you think you are better at using the right pronouns than when you started?
Why did you improve?


# [v0.2] [2016-11-26] Interview w/ Bill Ruplinger

What was difficult about the game?

    > sometimes the orange and yellow seem similar. didnt understand at the beginning. not all swiped got picked up

What was easy about the game?

    > once i understood the rules, its pretty easy
    
Do you think you are better at the game than when you started?

    > yes
    
Why did you improve?

    > started seeing the difference in the colors and recognize it was getting faster. try to anticipate
    
Would you play again?

    > no
    
General feedback

    > maybe for seniors not used to games, better introduction (maybe not timed behavior?)
    
What was difficult about the transgender transition in your family?
    
    > recognizing we now have a different gender grandchild. loss of one person, and accepting a new member of the family. and everything that goes with that. trying to be supportive of it... of her... support for her is the difficult part. 
    
    Q: what was difficult
    
        > understanding transgender issues. it was new trying to know what even terms should be used, how to relate to her and her issues. as well as understanding the broader social.cultural context of it. aware of it from reading newspaper in an abstract way, now it was brought home. many ways it was interesting. With Io and I we tried to be accepting of it and i think we did pretty well, its a change.

What was easy about it

    > 

How about pronouns

    > pronouns are still difficult for me. its really lack of being careful I very often call her john or he. I really need to make an effort to not do that. Im trying not do that, but I am. I think I messed up enough times this week, and im disappointed that im not able to fix it. 
    
    > No, I might have got worse. at first I was very conscious of it. but now i get comfortable and i easily slip back.
        
> I'd like to think more about the difficulties. 

Q: identifying with issues

    > trying to understand between her it might be easier if she were gay than transgender. and i struggle that maybe its a choice. trying to understand the difference and how anxious she was to become a woman. was a revealing experience to see all the others in thailand going through this. Also difficult that many transgender dont get SRS. these are just questions. relationship with sexuality. i realized transgender can be both gay or straight regardless of gender identiy. a lot of issues im interested in now as far as transgender comunity, because she struggles with this on a personal level, bot just abstract. stuff that interests me, doesnt say much about fiona.
    
Q: how does this effect her life in the future

    >Of course, I hope that she will come to terms with the fact she is transgender. I worry that she tries too much to be a woman, and she needs to come to terms with the fact aht she is transwoman, and i worry until she does that it will be difficult. and she has a lot of catching up to do, she is trying overly hard to be feminine and act how she expects a girl should. 
    also going back to thailand, but she just rejects other trans people and i think that is a difficult thing that she has to come to terms with and its part of her and think she will be a a stronger better person for realizing who she is as a transgender person. as far as being socially accepted, things have changed so quickly, i think it is easier than 2 or 5 years ago. if she were wiling to play the transcard, she could maybe even use it to her benefit. not passing judgement, but she probably could.
    
    > I think it would be good to have a way for people to even think about
    
    > first when we started telling people, it was difficult and i thought it would difficult for poeple to accept it and i was surprised how everyone was so open to it. idk what they were thinking but they were very understanding and interested and asked questions. I think it was really well received. as we went along i think it was easier to discuss with other people. 