# [v0.2] [2016-11-25] Interview w/ Carla The 
What was difficult about the game?

    > Telling the difference between the yellow and orange.
      it was difficult to tell when I would lose and I wasn't
      sure what the goal was and wasn't sure what the purple
      things were.

What was easy about the game?

    > Determining what to do was easy to figure out.

Do you think you are better at the game than when you started?

    > Definitely.

Why did you improve?

    > I improved because I knew what to expect, and as I
      got more experience, I developed strategies to swipe
      even more quickly. 
      
    Q. What were some of those strategies?
    
    > To start swiping as soon as I saw the square instead
      of waiting until they hit the bar.

Would you play again?

    > Probably not.
    
    Q. Why not?
    
    > It wasn't addicting enough, it wasn't like "Candy Crush".
      I quit in the middle because I felt like it would take
      a long time before I would fail. I felt like the
      difficulty didn't increase quickly enough and so I didn't
      feel too challenged.

General feedback

    > I thought the game was pretty impressive considering
      how quickly it was put together, perhaps what made
      Candy Crush more impressive is just the visual and
      design aspect of looking polished. This, to me, is what
      differentiates "Candy Crush" from other, less polished
      games.


# [v0.2] [2016-11-25] Interview w/ Meera Dhodapkar

## Internal Notes

- Started swiping left on the main screen.
- Kept asking
- "Man I can do this forever"
- "Is there a way to lose this game?"

## Interview

What was difficult about the game?

    > It was only difficult at the end, when the phone
      was buzzing more than the boosters were coming down.
      It got really distracting.

What was easy about the game?

    > It was a very simple game, there are not many
      components to the game.

Do you think you are better at the game than when you started?

    > No. Because there's not much to the game - it's just
      a question of how fast you can react to things like
      this.

Why did you improve?

    > Did not feel improvement.

Would you play again?

    > Maybe, It's probably one of those brainless activities 
      I could do.

General feedback

    > You should have a demo in the beginning. Otherwise
      no not really.
